# Function

## Introduction
  
**Instance of**: 

## Frequentist

**AKA**: $f: X \mapsto Y$, $f(x)$, map, mapping, linear map, linear function, transformation, morphism

**Distinct from**: 

**English**: A function from a set X to a set Y is an assignment of an element of Y to each element of X. The set X is the domain, and the set Y is the codomain.

**Formalization**:

The formalization is annoying in that there are multiple conventions for writing a function which are equivalent.

Psuedo code
```
f = function(X){
  Y=X+1 #some operation
  return(Y)
}
```
Where the domain is all flatoing point numbers and so is the codomain (up to the precision of the computer).

That can also be written.

$$
f: X \mapsto Y
$$
Where $f$ is the name of the function, $\mapsto$  is the "maps to" or "Maplet" symbol.
  
**Cites**: [Wikipedia]() ; [Wikidata]() ; [Wolfram]()
  
**Code**
    
::: panel-tabset
  
### R
[]()
  
Examples:
    
```{r}
```


### Python

[]()

Examples:
  
```{python}
```


### SQL

[]()

```{r}
library(DBI)
# Create an ephemeral in-memory RSQLite database
#con <- dbConnect(RSQLite::SQLite(), dbname = ":memory:")
#dbListTables(con)
#dbWriteTable(con, "mtcars", mtcars)
#dbListTables(con)

#Configuration failed because libpq was not found. Try installing:
#* deb: libpq-dev libssl-dev (Debian, Ubuntu, etc)
#install.packages('RPostgres')
#remotes::install_github("r-dbi/RPostgres")
#Took forever because my file permissions were broken
#pg_lsclusters
require(RPostgres)
# Connect to the default postgres database
#I had to follow these instructions and create both a username and database that matched my ubuntu name
#https://www.digitalocean.com/community/tutorials/how-to-install-postgresql-on-ubuntu-20-04-quickstart
con <- dbConnect(RPostgres::Postgres())

```

```{sql, connection=con}
```

### Torch

```{python}
import torch

```

:::

## Bayesian

**English**: 
**Formalization**:

$$
$$
  
Cites:

**Code**
  