# Hypothesis Testing

**Instance of**: joint probability

**AKA**: hypo testing

**Distinct from**: 

**English**: The probability of a hypothesis being true given the data.

* Not probability, but proportional to a probability [@etzIntroductionConceptLikelihood2017]


**Formalization**:

Written as a probability of a hypothesis being true, where the hypothesis is framed in values of a parameter


$$ 
\mathcal{L}(H|X)
$$

::: {.column-margin}
Where $H$ are the hypotheses, and $X$ is the evidence.
:::
 
    
**Cites**: [Wikipedia](https://en.wikipedia.org/wiki/Likelihood_function) ; [Wikidata]() ; [Wolfram]()
  
**Code**
    
::: panel-tabset
  
### R
[]()
  
Examples:
    
```{r}
```


### Python

[]()

Examples:
  
```{python}
```


### SQL

[]()

```{r}
library(DBI)
# Create an ephemeral in-memory RSQLite database
#con <- dbConnect(RSQLite::SQLite(), dbname = ":memory:")
#dbListTables(con)
#dbWriteTable(con, "mtcars", mtcars)
#dbListTables(con)

#Configuration failed because libpq was not found. Try installing:
#* deb: libpq-dev libssl-dev (Debian, Ubuntu, etc)
#install.packages('RPostgres')
#remotes::install_github("r-dbi/RPostgres")
#Took forever because my file permissions were broken
#pg_lsclusters
require(RPostgres)
# Connect to the default postgres database
#I had to follow these instructions and create both a username and database that matched my ubuntu name
#https://www.digitalocean.com/community/tutorials/how-to-install-postgresql-on-ubuntu-20-04-quickstart
con <- dbConnect(RPostgres::Postgres())

```

```{sql, connection=con}
```

### Torch

```{python}
import torch

```

:::
