# List (Sequence)

AKA: Sequence, $a_n$ where n is the nth element, (1,2,3, ....)

Distinct from: Set

Measure of:

Description: A list is a collection of objects with a specific ordering and where the same object can appear more than once. Call each object an element, and its location its index or rank. An index is a natural number counting upward from the first element in the list. Whether counting begins at 0 or 1 depends on local conventions.

Formalization:

Algorithm:

Cites: [Wikipedia](https://en.wikipedia.org/wiki/Sequence) [Wikidata](https://www.wikidata.org/wiki/Q36161) [Encyclopedia Of Math](http://encyclopediaofmath.org/index.php?title=Sequence&oldid=48671) [Wolfram](https://mathworld.wolfram.com/Sequence.html)
[PlanetMath](https://planetmath.org/sequence)

::: panel-tabset

## R

Documentation:

[list: Lists -- Generic and Dotted Pairs](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/list)

Examples:

```{r}
example_list = list(1,2,3)
example_list
```

## Python

Documentation:

[More on Lists](https://docs.python.org/3/tutorial/datastructures.html)

Examples:

```{python}
example_list =  [1,2,3]
example_list
```

## SQL

```{r}
library(DBI)
# Create an ephemeral in-memory RSQLite database
con <- dbConnect(RSQLite::SQLite(), dbname = ":memory:")
dbListTables(con)
dbWriteTable(con, "mtcars", mtcars)
dbListTables(con)
```

```{sql, connection=con}
create table StatisticalNumbers(
 value int
)
```


```{sql, connection=con}
SELECT * FROM mtcars LIMIT 5;
```

:::