# NULL {.unnumbered}

**Instance of**: 

**AKA**: null, NULL

**Distinct from**: 

**English**: 

**Formalization**:

$$ 
$$

**Cites**: [Wikipedia Null (SQL)](https://en.wikipedia.org/wiki/Null_(SQL))) ; [Wikidata Q371029](https://www.wikidata.org/wiki/Q371029) 

[R null values: NULL, NA, NaN, Inf](https://www.r-bloggers.com/2018/07/r-null-values-null-na-nan-inf/)

**Code**

{{< include ../../include_toy_data.qmd >}}

## R

#### Base {.unnumbered}

[The Null Object](https://stat.ethz.ch/R-manual/R-devel/library/base/html/NULL.html)

```{r}

class(NULL)
is.null(NULL)
length(NULL)

is.null(list())     # FALSE (on purpose!)
is.null(pairlist()) # TRUE
is.null(integer(0)) # FALSE
is.null(logical(0)) # FALSE
as.null(list(a = 1, b = "c"))

```

#### Tidyverse {.unnumbered}

[Is object an empty vector or NULL?](https://rdrr.io/github/tidyverse/rlang/man/is_empty.html)

```{r}
is_empty(NULL)
is_empty(list())
is_empty(list(NULL))

NULL==NA
NULL==6

```

[Default value for NULL](https://rlang.r-lib.org/reference/op-null-default.html)

```{r}

#Replace Nulls
1 %||% 2
NULL %||% 2

```

#### DataTable {.unnumbered}

[]()

```{r}
```

#### Arrow {.unnumbered}

[Apache Arrow data types](https://arrow.apache.org/docs/r/reference/data-type.html)
"These functions create type objects corresponding to Arrow types. Use them when defining a schema() or as inputs to other types, like struct. Most of these functions don't take arguments, but a few do."

```{r}

null()

```

## Python

#### 3.x / math/ statistics


[None](https://docs.python.org/3/library/constants.html)
[Python None Keyword](https://www.w3schools.com/python/ref_keyword_none.asp)

None
An object frequently used to represent the absence of a value, as when default arguments are not passed to a function. Assignments to None are illegal and raise a SyntaxError. None is the sole instance of the NoneType type.


```{python}

type(None)

None is True

None is False

try:
print(len(None))
except Exception as ex:
print(ex)

```

```{python}

try:
print(len(None)) #None has no length
except Exception as ex:
print(ex)

```


#### NumPy / SciPy / scikit-learn

[]()

```{python}

np.array([[ None,  None],
        [ None,  None]])

np.array([[ None,  None],
        [ None,  None]], dtype=bool)

```

#### Pandas

[]()

```{python}

pd.Series([None, None])

pd.Series([None, None]).isnull()

pd.Series([1, None]).notnull()


```

## Jax

```{python}

jnp.array([[ None,  None],
         [ None,  None]])

```

## Numpyro

Uses jax's boolean array

```{python}
```

## Stan

[]()

```{r}
```

## Torch

[TORCH.NAN_TO_NUM](https://pytorch.org/docs/stable/generated/torch.nan_to_num.htmll)

```{python}

torch.tensor([float('nan'), float('inf'), -float('inf'), 3.14])

try:
  print(torch.tensor([None])) #Fails
except Exception as ex:
  print(ex)
  
```

## Tensorflow

[]()

```{python}

tf.constant([5.0, np.nan, 6.8, np.nan, np.inf])

tf.math.is_nan(tf.constant([5.0, np.nan, 6.8, np.nan, np.inf]))

try:
  print(tf.constant([None,None], dtype=tf.bool))
except Exception as ex:
  print(ex)


```

## PostgreSQL

[]()


```{sql, connection=con_Postgres, cache=F}

DROP TABLE IF EXISTS null_df;

```

```{sql, connection=con_Postgres, cache=F}

CREATE TABLE IF NOT EXISTS null_df (
example_null boolean,
example_notnull boolean NOT NULL
);

```

Error: Failed to fetch row: ERROR:  null value in column "example_notnull" of relation "null_df" violates not-null constraint
DETAIL:  Failing row contains (t, null).

```{sql, connection=con_Postgres, cache=F, eval=F}

INSERT INTO null_df (example_null, example_notnull)
VALUES
(NULL, False),
(TRUE, NULL);
;

```

```{sql, connection=con_Postgres, cache=F, eval=F}

INSERT INTO null_df (example_null, example_notnull)
VALUES
(NULL, False),
(TRUE, TRUE);
;

```


```{sql, connection=con_Postgres, cache=F}

SELECT * from null_df;

```

## DuckDB

[Boolean Type](https://duckdb.org/docs/sql/data_types/boolean.html)

```{sql, connection=con_duckdb, cache=F}

DROP TABLE IF EXISTS null_df;

```

```{sql, connection=con_duckdb, cache=F}

CREATE TABLE IF NOT EXISTS null_df (
example_null boolean,
example_notnull boolean NOT NULL
);

```

Error: rapi_execute: Failed to run query
Error: Constraint Error: NOT NULL constraint failed: null_df.example_notnull
Failed to execute SQL chunk

```{sql, connection=con_duckdb, cache=F, eval=F}

INSERT INTO null_df (example_null, example_notnull)
VALUES
(NULL, False),
(TRUE, NULL);
;

```

```{sql, connection=con_duckdb, cache=F, eval=F}

INSERT INTO null_df (example_null, example_notnull)
VALUES
(NULL, False),
(TRUE, TRUE);
;

```


```{sql, connection=con_duckdb, cache=F}

SELECT * from null_df;

```


