# Bayesianism  {.unnumbered}

# {.unnumbered}

## Introduction
  
**Instance of**: 

**AKA**: 

**Distinct from**: 

**English**: 

**Formalization**:

The posterior, $P(H|E)$, is our final credibility over possible states of the world given the evidence we've observed. Our prior, $P(H)$, is the starting credibility we assigned to those states. The marginal, $P(E)$, is the probability of observing the evidence on average across all the possible states. The likelihood, P(E|H), is the probability of observing that evidence given a particular state of the world is true.

$$ 
P(H|E) = P(H) \times \frac{P(E|H)}{P(E)}
$$
    
    
**Cites**: [Wikipedia]() ; [Wikidata]() ; [Wolfram]()
  
**Code**
    
::: panel-tabset
  
### R
[]()
  
Examples:
    
```{r}
```


### Python

[]()

Examples:
  
```{python}
```


### SQL

[]()

```{r}
library(DBI)
# Create an ephemeral in-memory RSQLite database
#con <- dbConnect(RSQLite::SQLite(), dbname = ":memory:")
#dbListTables(con)
#dbWriteTable(con, "mtcars", mtcars)
#dbListTables(con)

#Configuration failed because libpq was not found. Try installing:
#* deb: libpq-dev libssl-dev (Debian, Ubuntu, etc)
#install.packages('RPostgres')
#remotes::install_github("r-dbi/RPostgres")
#Took forever because my file permissions were broken
#pg_lsclusters
require(RPostgres)
# Connect to the default postgres database
#I had to follow these instructions and create both a username and database that matched my ubuntu name
#https://www.digitalocean.com/community/tutorials/how-to-install-postgresql-on-ubuntu-20-04-quickstart
con <- dbConnect(RPostgres::Postgres())

```

```{sql, connection=con}
```

### Torch

```{python}
import torch

```

:::

## Bayesian

**English**: 
**Formalization**:

$$
$$
  
Cites:

**Code**
  
    